A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds

### 2013-06-03 paper/paper.tex
fixed table

\begin{dfn}[Hops] Suppose $\tau$ is a 2-simplex in $M$ and $v_1$ and $v_2$ are vertices in $M$ such that $v_1*\tau$ and $v_2*\tau$ are 3-simplices in $M$. The PL-path from $v_1$ through the barycenter of $\tau$ and ending on $v_2$ will be called a \textbf{hop} from $v_1$ to $v_2$. See Figure \ref{fig:hop}. TO DO: FIX THIS FIG NUM
\end{dfn}

@@

Here is a table of the number of triangulations in the census at each topological type and diameter. TO DO: CHANGE ORDER OF MANIFOLDS IN TABLE TO S3/Q, L(4,1), L(3,1), RP3, S3. TO DO: PUT EACH POSSIBLE DIAMETER IN TABLE ON ITS OWN COLUMN (TO ALIGN THEM WITH LABELS ON THE LEFT...) \vspace{.1in}

\begin{tabular} {| l l | l l | l l | l l | l l |}
\hline
\multicolumn{2}{|c|}{$S^{3}/Q$} &
\multicolumn{2}{|c|}{$L(3,1)$} &
\multicolumn{2}{|c|}{$RP^{3}$} &
\multicolumn{2}{|c|}{$S^{3}$} &
\multicolumn{2}{|c|}{$L(4,1)$} \\
\hline
\hline
$1H$&1    &$2E$&1    &$1H$&10    &$1E$&3    &$1J$&1 \\
  &       &$1J$&1    &$2E$&7     &$1H$&173  &    &  \\
  &       &  &       &$1J$&5     &$2E$&401  &    &  \\
  &       &  &       &    &      &$1J$&2438 &    &  \\
  &       &  &       &    &      &$3E$&1060 &    &  \\
  &       &  &       &    &      &$2H$&582  &    &  \\
  &       &  &       &    &      &$4E$&93   &    &  \\
  &       &  &       &    &      &$2J$&11   &    &  \\
\hline
\end{tabular}

\noindent Here is a table of the number of triangulations at each diameter. TO DO: MAKE THIS A "TOTAL" COLUMN IN PREVIOUS TABLE.\vspace{.1in}

\begin{tabular} {| l l |}
\hline
$1E$ &       3\\
$1H$ &       184\\
$2E$ &       409\\
$1J$ &       2445\\
$3E$ &       1060\\
$2H$ &       582\\
$4E$ &       93\\
$2J$ &       11\\
\hline
\end{tabular}

>>>>

\begin{dfn}[Hops] Suppose $\tau$ is a 2-simplex in $M$ and $v_1$ and $v_2$ are vertices in $M$ such that $v_1*\tau$ and $v_2*\tau$ are 3-simplices in $M$. The PL-path from $v_1$ through the barycenter of $\tau$ and ending on $v_2$ will be called a \textbf{hop} from $v_1$ to $v_2$. See Figure \ref{fig:hop}. TO DO: FIX THIS FIG NUM  VADAS: I THINK THIS IS DUE TO AMSTHM AND I``M NOT SURE HOW TO FIX IT.
\end{dfn}

@@

Here is a table of the number of triangulations in the census at each topological type and diameter. \vspace{.1in}

\begin{tabular} {| c | c | c | c | c | c | c |}
    \hline
Diameter & $S^{3}/Q$ & $L(4,1)$ & $L(3,1)$ & $RP^{3}$ & $S^{3}$ & Total \\
\hline
\hline
$1E$&  &  &  &   &3    & 3    \\
$1H$&1 &  &  &10 &173  & 184  \\
$2E$&  &  &1 &7  &401  & 409  \\
$1J$&  &1 &1 &5  &2438 & 2445 \\
$3E$&  &  &  &   &1060 & 1060 \\
$2H$&  &  &  &   &582  & 582  \\
$4E$&  &  &  &   &93   & 93   \\
$2J$&  &  &  &   &11   & 11   \\
\hline
Total&1 &1 &2 &22   &4761   &4787  \\
\hline
\end{tabular}

\noindent Here is a table of the number of triangulations at each diameter.
